The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-11-30 Paper.qmd
Moved PCA code into analysis.R

The anonymized data used in the study are available at https://github.com/grasshoppermouse/utiladata2023. Study code is available at https://github.com/michaelrgaffney/utilasignaling.

>>>>

The anonymized data used in the study are available at <https://github.com/grasshoppermouse/utiladata2023>. Study code is available at <https://github.com/michaelrgaffney/utilasignaling>.
